PANCHANGE_analysis

### 2020-08-26 PANCHANGE_analysis.Rmd
added key_worker and highest_education

```{r Ethnicity_collapsed by Sample prop plot}
Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = Ethnicity_collapsed,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Ethnicity_collapsed",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

@@

```{r Gender_collapsed by Sample prop plot}
Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = Gender_collapsed,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Gender_collapsed",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

@@

```{r highest_education per Sample prop cross table}
dat %>%
  group_by(Sample) %>%
  count(highest_education, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))
```

```{r highest_education per Sample count cross table}
dat %>%
  count(highest_education, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )
```

```{r highest_education per Sample chisquare test}
dat %>%
  count(highest_education, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-highest_education) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()
```

```{r highest_education by Sample count plot}
highest_education_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = highest_education,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "highest_education",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()
```

```{r highest_education by Sample prop plot}
highest_education_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = highest_education,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "highest_education",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()
```

@@

```{r key_worker per Sample prop cross table}
dat %>%
  group_by(Sample) %>%
  count(key_worker, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))
```

```{r key_worker per Sample count cross table}
dat %>%
  count(key_worker, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )
```

```{r key_worker per Sample chisquare test}
dat %>%
  count(key_worker, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-key_worker) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()
```

```{r key_worker by Sample count plot}
key_worker_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = key_worker,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "key_worker",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()
```

```{r key_worker by Sample prop plot}
key_worker_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = key_worker,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "key_worker",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()
```

>>>>

```{r Ethnicity_collapsed by Sample prop plot}
Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = Ethnicity_collapsed,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Ethnicity_collapsed",
    y = "Percentage per sample",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

@@

```{r Gender_collapsed by Sample prop plot}
Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = Gender_collapsed,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Gender_collapsed",
    y = "Percentage per sample",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

@@

```{r highest_education per Sample prop cross table}
highest_education_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(highest_education, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

kable(highest_education_per_Sample_prop_Sample_cross_table)
highest_education_per_Sample_prop_Sample_cross_table
```

```{r highest_education per Sample count cross table}
highest_education_per_Sample_count_cross_table <- dat %>%
  count(highest_education, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )

kable(highest_education_per_Sample_count_cross_table)
highest_education_per_Sample_count_cross_table
```

```{r highest_education per Sample chisquare test}
highest_education_per_Sample_chissquare_test <- dat %>%
  count(highest_education, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-highest_education) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()

kable(highest_education_per_Sample_chissquare_test)
highest_education_per_Sample_chissquare_test
```

```{r highest_education by Sample count plot}
highest_education_by_Sample_count_plot <- highest_education_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = highest_education,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "highest_education",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

highest_education_by_Sample_count_plot
```

```{r highest_education by Sample prop plot}
highest_education_by_Sample_prop_plot <- highest_education_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = highest_education,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "highest_education",
    y = "Percentage per sample",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

highest_education_by_Sample_prop_plot
```

@@

```{r key_worker per Sample prop cross table}
key_worker_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(key_worker, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

kable(key_worker_per_Sample_prop_Sample_cross_table)
key_worker_per_Sample_prop_Sample_cross_table
```

```{r key_worker per Sample count cross table}
key_worker_per_Sample_count_cross_table <- dat %>%
  count(key_worker, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )

kable(key_worker_per_Sample_count_cross_table)
key_worker_per_Sample_count_cross_table
```

```{r key_worker per Sample chisquare test}
key_worker_per_Sample_chissquare_test <- dat %>%
  count(key_worker, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-key_worker) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()

kable(key_worker_per_Sample_chissquare_test)
key_worker_per_Sample_chissquare_test
```

```{r key_worker by Sample count plot}
key_worker_by_Sample_count_plot <- key_worker_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = key_worker,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "key_worker",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

key_worker_by_Sample_count_plot
```

```{r key_worker by Sample prop plot}
key_worker_by_Sample_prop_plot <- key_worker_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = key_worker,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "key_worker",
    y = "Percentage per sample",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

key_worker_by_Sample_prop_plot
```
